Deciding Bitvector Termination with Program Synthesis

### 2014-06-25 papers/termination/paper.tex
revised sec 6

Limitations: 
\begin{itemize}
\item No recursion.
\item Nested loops.
\end{itemize}

@@

\section{Solving the Synthesis Formula} \label{sec:synthesis}
We can solve the synthesis problem using any off-the-shelf program synthesiser.  If you don't
have a program synthesiser kicking around, we present the design of one synthesiser
that can be used to solve the problem.

\iffalse
\subsection{The Search Space and the Kolmogorov Complexity of a Ranking Function}
\begin{conjecture}
The lexicographic ordering does not influence the size of the search space. Thus, finding potentially lexicographic termination arguments is not more difficult than finding non-lexicographic ones.   
\end{conjecture}

As a consequence of the aforementioned conjecture, we do not need to commit to a specific form of the termination argument. While other approaches, e.g. \cite{DBLP:conf/tacas/LeikeH14}, 
conduct independent searches for each possible form of the ranking function with some of them futile whenever the assumed constrained ranking function does not exist, we have a single search that aims at finding the ranking function with the lowest Kolmogorov complexity. 
\fi

\input{kalashnikov}

>>>>

Limitations: 
\begin{itemize}
\item No recursion.
\item Nested loops.
\item Heap.
\end{itemize}

@@

\section{Solving the Synthesis Formula} \label{sec:synthesis}
%
\iffalse
\subsection{The Search Space and the Kolmogorov Complexity of a Ranking Function}
\begin{conjecture}
The lexicographic ordering does not influence the size of the search space. Thus, finding potentially lexicographic termination arguments is not more difficult than finding non-lexicographic ones.   
\end{conjecture}

As a consequence of the aforementioned conjecture, we do not need to commit to a specific form of the termination argument. While other approaches, e.g. \cite{DBLP:conf/tacas/LeikeH14}, 
conduct independent searches for each possible form of the ranking function with some of them futile whenever the assumed constrained ranking function does not exist, we have a single search that aims at finding the ranking function with the lowest Kolmogorov complexity. 
\fi
%
%
\input{kalashnikov}
